
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Computational Methods}
\label{ac:computation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{GitHub Repository}
All \textit{Mathematica} notebooks, programs, and algorithms used within this work are freely available for use or modification and can be found at: 
\begin{center}
	\url{https://github.com/phelpsmatthew/Cosmological-Fluctuations}
\end{center}

\section{\textit{Mathematica} and \textit{xAct}}

In composing the fluctuations equations in cosmology, there are numerous steps that pose enormous difficulty to being able to do calculations non-computationally, largely attributed to the sheer number of terms and manipulations involved. Such factors include dummy index refactoring, commutation of covariant derivatives, expressing curvature tensors as Christoffel symbols (functions of the metric), performing a 3+1 splitting of the fluctuations, substituting the SVT decomposition of the perturbed metric, collecting combinations of SVT components to form gauge invariants, testing covariant conservation, performing conformal transformations, and evaluating the fluctuations within an explicit choice of coordinate basis.

As the focus of this thesis revolves around the discussion of the underlying physics and not the means of computation, the equations given in the main body have been presented in a significantly reduced form, with all auxiliary computations hidden. However, it is of practical interest to demonstrate how such calculations are performed. Therefore, to serve as a representative example, in Sec. \ref{s:calc_example} we present a mostly-complete A to Z calculation of a SVT3 Roberston Walker $k\ne 0$ gauge invariant formulation of the Einstein fluctuation equations.

Before illustrating an example calculation, we describe the computational tools underlying the results in this thesis. In the field of cosmological perturbations, one needs software capable of doing abstract symbolic tensor calculus on curved manifolds. In regard to symbolic computation alone, the \textit{Wolfram Mathematica} language serves as one of the most effective frameworks for doing so, with especially large popularity and support within the fields theoretical physics and mathematics. Natively, \textit{Mathematica} does not provide support for GR specific applications and therefore one must turn to user-created 3rd-party packages that have been developed for use within \textit{Mathematica}. To fulfill this need, the package \textit{xAct} \cite{garcia_2002}, developed originally by José M. Martín-García, provides a powerful set of methods and capabilities for performing abstract tensor calculus within GR. It is composed of a suite of free packages that implement state-of-the-art algorithms for fast manipulation of indices in a highly programmable and configurable form. The set of packages used within this work, along with their purpose is described below (for more information, cf. \cite{garcia_2002}). 

\begin{itemize}
	\item \textit{xTensor}: Provides core functionality and capabilities in abstract tensor calculus within General Relativity. Works with tensors with arbitrary symmetries under permutations of indices, defined on specified manifolds (or even several different manifolds). It computes covariant derivatives, Lie derivatives and parametric derivatives. Additionally it allows the presence of a metric in each manifold and defines all the associated tensors (Riemann, Ricci, Einstein, Weyl, etc.)
	%
	\item \textit{xCoba}: Provides several tools for working with bases and components. It allows one to define bases on one or more manifolds and to handle basis vectors, using basis indices notation. It performs component calculations such as expanding a tensor in a specified basis, changing the basis of an expression or tracing the contraction of basis dummies. The package knows how to express derivatives and brackets of basis vectors in terms of Christoffel and torsion tensors and how to assign values to the components of a tensor.
	%
	\item \textit{xPert}: Used for fast construction and manipulation of the equations of metric perturbation theory. Based on the use of explicit formulas for the construction of the $n$-th order perturbation of the most relevant curvature tensors.
	%
	\item \textit{TexAct}: Produces nice TeX code for tensor expressions. For any given tensor expression, the command \textit{TexPrint} produces a single string with tensors, indices, derivatives, etc. formatted as one would express within in an article. A second command \textit{TexBreak} allows breaking this string in various lines in a highly flexible way; this function can also make line-breaks according to the lengths of the actual typeset expressions. Lists of equations can be typeset with automatic line breaking and alignment.
	%
	\item \textit{xTras} \cite{nutma_2014}: Provides functions and methods frequently needed when doing (classical) field theory, e.g. Killing vectors, symmetrizing covariant derivatives, converting contractions of Riemann tensors to Ricci tensors.
\end{itemize}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Detailed Calculation Example}
\label{s:calc_example}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
To convey the methods and procedural steps underyling computations within perturbative cosmology, here we calculate the perturbed Einstein equations of motion within a Roberton Walker background with unspecified 3-curvature $k$. All steps, including simplifications, are done entirely programmatically. 

\subsection{Conformal Transformation and Perturbation of $G_{\mu\nu}$}
As we seek to describe the perturbed $\delta G_{\mu\nu}$ within the Roberston Walker geometry
\begin{eqnarray}
ds^2 &=& \Omega^2(\tau)\tilde g_{\mu\nu} dx^\mu dx^\nu,\qquad 
\tilde g_{\mu\nu} = \text{diag}\left(-1,\frac{1}{1-kr^2},r^2,r^2\sin^2\theta\right),
\label{ac_rw_metric}
\end{eqnarray}
we need to determine the form of $\delta G_{\mu\nu}$ under conformal transformation. To this end, we begin with the full $G_{\mu\nu} = R_{\mu\nu} - \tfrac12 g_{\mu\nu} R$ and express the curvature tensors in terms of the Christoffel symbols,
\begin{eqnarray}
G_{\mu\nu} &=& - \Gamma^{\alpha }{}_{\mu \beta } \Gamma^{\beta }{}_{\alpha \nu } + \Gamma^{\alpha }{}_{\alpha \beta } \Gamma^{\beta }{}_{\mu \nu } + R_{\mu \nu } \nonumber \\ 
&& -  \tfrac{1}{2} g_{\mu \nu } \bigl(g^{\alpha \beta } (\Gamma^{\gamma }{}_{\gamma \zeta } \Gamma^{\zeta }{}_{\alpha \beta } -  \Gamma^{\gamma }{}_{\alpha \zeta } \Gamma^{\zeta }{}_{\gamma \beta } + R[\partial ]_{\alpha \beta }
\nonumber\\
&& -  \partial_{\alpha }\Gamma^{\gamma }{}_{\gamma \beta } + \partial_{\gamma }\Gamma^{\gamma }{}_{\alpha \beta })\bigr) + \partial_{\alpha }\Gamma^{\alpha }{}_{\mu \nu } -  \partial_{\mu }\Gamma^{\alpha }{}_{\alpha \nu }.
\label{G_gamma}
\end{eqnarray}
Under conformal transformation $g_{\mu\nu} \to \Omega^2(x)\tilde g_{\mu\nu}$, the Christoffel symbol transforms as
\begin{eqnarray}
\Gamma^{\lambda}_{\mu\nu} \to \tilde\Gamma^{\lambda}_{\mu\nu} + \Omega^{-1}(\delta^\lambda_\nu \tilde \nabla_\mu + \delta^\lambda_\mu \tilde\nabla_\nu - \tilde g_{\mu\nu}  \tilde g^{\lambda\sigma}\tilde \nabla_\sigma)\Omega(x),
\label{gamma_conf}
\end{eqnarray}
where $\tilde \Gamma^\lambda_{\mu\nu}$ is evaluated within the geometry $\tilde g_{\mu\nu}$. Now, transforming $g_{\mu\nu} \to \Omega^2(x)\tilde g_{\mu\nu}$ and \eqref{gamma_conf} within \eqref{G_gamma}, we find that under conformal transformation $G_{\mu\nu}$ transforms into
\begin{eqnarray}
G_{\mu\nu} &\to& \tilde G_{\mu\nu} - \tfrac{1}{2} \tilde g_{\mu \nu } \tilde R^{\alpha }{}_{\alpha } + \tilde R_{\mu \nu } - 2 \tilde g_{\mu \nu } \Omega^{-1} \tilde \nabla_{\alpha }\tilde \nabla^{\alpha }\Omega + \tilde g_{\mu \nu } \Omega^{-2} \tilde \nabla_{\alpha }\Omega \tilde\nabla^{\alpha }\Omega. 
\nonumber\\
 &&- 4 \Omega^{-2} \tilde \nabla_{\mu }\Omega \tilde\nabla_{\nu }\Omega + 2 \Omega^{-1} \tilde \nabla_{\nu }\tilde \nabla_{\mu }\Omega .
\end{eqnarray}
To determine the fluctuation of $G_{\mu\nu}$, we need to perturb the metric according to $g_{\mu\nu} = g^{(0)}_{\mu\nu} + h_{\mu\nu} + \mathcal O(h^2)+ ...$, keeping terms only up to first order. Denoting $h_{\mu\nu} \equiv \Omega^2(x) f_{\mu\nu}$, we obtain
\begin{eqnarray}
\delta  G_{\mu\nu}&=& - \tfrac{1}{2} f_{\mu \nu } \tilde R + \tfrac{1}{2} \tilde g_{\mu \nu } f^{\alpha \beta } \tilde R_{\alpha \beta } + \tfrac{1}{2} \tilde\nabla_{\alpha }\tilde\nabla^{\alpha }f_{\mu \nu } -  \tfrac{1}{2} \tilde g_{\mu \nu } \tilde\nabla_{\alpha }\tilde\nabla^{\alpha }f - 2 f_{\mu \nu } \Omega^{-1} \tilde\nabla_{\alpha }\tilde\nabla^{\alpha }\Omega 
\nonumber\\
&&-  \tfrac{1}{2} \tilde\nabla_{\alpha }\tilde\nabla_{\mu }f_{\nu }{}^{\alpha }-  \tfrac{1}{2} \tilde\nabla_{\alpha }\tilde\nabla_{\nu }f_{\mu }{}^{\alpha } -  \tilde g_{\mu \nu } \Omega^{-1} \tilde\nabla_{\alpha }\Omega \tilde\nabla^{\alpha }f + \Omega^{-1} \tilde\nabla_{\alpha }f_{\mu \nu } \tilde\nabla^{\alpha }\Omega  
\nonumber\\
&&+ f_{\mu \nu } \Omega^{-2} \tilde\nabla_{\alpha }\Omega \tilde\nabla^{\alpha }\Omega  + 2 \tilde g_{\mu \nu } \Omega^{-1} \tilde\nabla^{\alpha }\Omega \tilde\nabla_{\beta }f_{\alpha }{}^{\beta } + \tfrac{1}{2} \tilde g_{\mu \nu } \tilde\nabla_{\beta }\tilde\nabla_{\alpha }f^{\alpha \beta }  
\nonumber\\
&&+ 2 \tilde g_{\mu \nu } f^{\alpha \beta } \Omega^{-1} \tilde\nabla_{\beta }\tilde\nabla_{\alpha }\Omega -  \tilde g_{\mu \nu } f_{\alpha \beta } \Omega^{-2} \tilde\nabla^{\alpha }\Omega \tilde\nabla^{\beta }\Omega \nonumber \\ 
&& -  \Omega^{-1} \tilde\nabla^{\alpha }\Omega \tilde\nabla_{\mu }f_{\nu \alpha } -  \Omega^{-1} \tilde\nabla^{\alpha }\Omega \tilde\nabla_{\nu }f_{\mu \alpha } + \tfrac{1}{2} \tilde\nabla_{\nu }\tilde\nabla_{\mu }f,
\label{dg_conf}
\end{eqnarray}
representing the perturbed Einstein tensor in a generic conformal geometry. In order to express \eqref{dg_conf} in the SVT3 basis, it must be prepared according to the 3+1 decomposition. Here we perform a splitting via a a projection based on the four vector $U^\alpha$ as outlined in Sec. \ref{aas:3_1_decomp}. We evaluate $\tilde g_{00} = -1$ and express all 3-space curvature tensors in terms of $k$. Finally, we decompose $\delta G_{\mu\nu}$ itself according to the 3+1 decomposition to obtain
\begin{eqnarray}
\delta G_{00}&=& k \tilde{g}^{ba} f_{ab} + 3 k f_{00}{} -  \dot{f}_{00}{} \dot{\Omega} \Omega^{-1} -  \dot{f} \dot{\Omega} \Omega^{-1} - 2 \dot{\Omega} \tilde{g}^{ba} f_{0}{}_{b} \Omega^{-2} \tilde{\nabla}_{a}\Omega  
\nonumber\\
&&+ 4 \tilde{g}^{ba} f_{0}{}_{a} \Omega^{-1} \tilde{\nabla}_{b}\dot{\Omega} + \tilde{g}^{ba} \Omega^{-1} \tilde{\nabla}_{a}\Omega \tilde{\nabla}_{b}f_{00}{} + 2 \dot{\Omega} \tilde{g}^{ba} \Omega^{-1} \tilde{\nabla}_{b}f_{0}{}_{a} 
\nonumber\\
&& + \tilde{g}^{ba} \Omega^{-1} \tilde{\nabla}_{a}f \tilde{\nabla}_{b}\Omega + \tilde{g}^{ca} \tilde{g}^{db} f_{cd} \Omega^{-2} \tilde{\nabla}_{a}\Omega \tilde{\nabla}_{b}\Omega  + \tilde{g}^{ba} f_{00}{} \Omega^{-2} \tilde{\nabla}_{a}\Omega \tilde{\nabla}_{b}\Omega  
\nonumber\\
&&+ \tfrac{1}{2} \tilde{g}^{ba} \tilde{\nabla}_{b}\tilde{\nabla}_{a}f_{00}{} + \tfrac{1}{2} \tilde{g}^{ba} \tilde{\nabla}_{b}\tilde{\nabla}_{a}f  - 2 \tilde{g}^{ba} f_{00}{} \Omega^{-1} \tilde{\nabla}_{b}\tilde{\nabla}_{a}\Omega  
\nonumber\\
&&- 2 \tilde{g}^{ca} \tilde{g}^{db} \Omega^{-1} \tilde{\nabla}_{a}\Omega \tilde{\nabla}_{d}f_{cb} -  \tfrac{1}{2} \tilde{g}^{ca} \tilde{g}^{db} \tilde{\nabla}_{d}\tilde{\nabla}_{c}f_{ab}  
- 2 \tilde{g}^{ca} \tilde{g}^{db} f_{ab} \Omega^{-1} \tilde{\nabla}_{d}\tilde{\nabla}_{c}\Omega 
\nonumber\\
\\
\delta G_{0i}&=& 3 k f_{0}{}_{i} -  \dot{\Omega}^2 f_{0}{}_{i} \Omega^{-2} + 2 \overset{..}{\Omega} f_{0}{}_{i} \Omega^{-1} -  \dot{f}_{ib} \tilde{g}^{ba} \Omega^{-1} \tilde{\nabla}_{a}\Omega -  \tfrac{1}{2} \tilde{g}^{ba} \tilde{\nabla}_{b}\dot{f}_{ia}  
\nonumber\\
&&+ \tilde{g}^{ba} \Omega^{-1} \tilde{\nabla}_{a}\Omega \tilde{\nabla}_{b}f_{0}{}_{i} + \tilde{g}^{ba} f_{0}{}_{i} \Omega^{-2} \tilde{\nabla}_{a}\Omega \tilde{\nabla}_{b}\Omega + \tfrac{1}{2} \tilde{g}^{ba} \tilde{\nabla}_{b}\tilde{\nabla}_{a}f_{0}{}_{i} 
\nonumber\\
&& - 2 \tilde{g}^{ba} f_{0}{}_{i} \Omega^{-1} \tilde{\nabla}_{b}\tilde{\nabla}_{a}\Omega -  \tfrac{1}{2} \tilde{g}^{ba} \tilde{\nabla}_{b}\tilde{\nabla}_{i}f_{0}{}_{a} + \tfrac{1}{2} \tilde{\nabla}_{i}\dot{f}_{00}{} + \tfrac{1}{2} \tilde{\nabla}_{i}\dot{f}  
\nonumber\\
&&+ \dot{\Omega} \Omega^{-1} \tilde{\nabla}_{i}f_{00}{} -  \tilde{g}^{ba} \Omega^{-1} \tilde{\nabla}_{a}\Omega \tilde{\nabla}_{i}f_{0}{}_{b}
\\
\nonumber\\
\delta G_{ij}&=& - \tfrac{1}{2} \overset{..}{f}_{ij} + \tfrac{1}{2} \overset{..}{f}_{00}{} \tilde{g}_{ij} + \tfrac{1}{2} \overset{..}{f} \tilde{g}_{ij} -  k \tilde{g}^{ba} \tilde{g}_{ij} f_{ab} + 3 k f_{ij} -  \dot{\Omega}^2 f_{ij} \Omega^{-2} -  \dot{\Omega}^2 \tilde{g}_{ij} f_{00}{} \Omega^{-2} 
\nonumber\\
&& -  \dot{f}_{ij} \dot{\Omega} \Omega^{-1}  + 2 \dot{f}_{00}{} \dot{\Omega} \tilde{g}_{ij} \Omega^{-1} + \dot{f} \dot{\Omega} \tilde{g}_{ij} \Omega^{-1} + 2 \overset{..}{\Omega} f_{ij} \Omega^{-1} + 2 \overset{..}{\Omega} \tilde{g}_{ij} f_{00}{} \Omega^{-1} 
\nonumber\\
&& + 2 \dot{\Omega} \tilde{g}^{ba} \tilde{g}_{ij} f_{0}{}_{b} \Omega^{-2} \tilde{\nabla}_{a}\Omega  - 2 \dot{f}_{0}{}_{b} \tilde{g}^{ba} \tilde{g}_{ij} \Omega^{-1} \tilde{\nabla}_{a}\Omega -  \tilde{g}^{ba} \tilde{g}_{ij} \tilde{\nabla}_{b}\dot{f}_{0}{}_{a} 
\nonumber\\
&& - 4 \tilde{g}^{ba} \tilde{g}_{ij} f_{0}{}_{a} \Omega^{-1} \tilde{\nabla}_{b}\dot{\Omega} + \tilde{g}^{ba} \Omega^{-1} \tilde{\nabla}_{a}\Omega \tilde{\nabla}_{b}f_{ij} \nonumber \\ 
&& - 2 \dot{\Omega} \tilde{g}^{ba} \tilde{g}_{ij} \Omega^{-1} \tilde{\nabla}_{b}f_{0}{}_{a} -  \tilde{g}^{ba} \tilde{g}_{ij} \Omega^{-1} \tilde{\nabla}_{a}f \tilde{\nabla}_{b}\Omega -  \tilde{g}^{ca} \tilde{g}^{db} \tilde{g}_{ij} f_{cd} \Omega^{-2} \tilde{\nabla}_{a}\Omega \tilde{\nabla}_{b}\Omega \nonumber \\ 
&& + \tilde{g}^{ba} f_{ij} \Omega^{-2} \tilde{\nabla}_{a}\Omega \tilde{\nabla}_{b}\Omega + \tfrac{1}{2} \tilde{g}^{ba} \tilde{\nabla}_{b}\tilde{\nabla}_{a}f_{ij} -  \tfrac{1}{2} \tilde{g}^{ba} \tilde{g}_{ij} \tilde{\nabla}_{b}\tilde{\nabla}_{a}f - 2 \tilde{g}^{ba} f_{ij} \Omega^{-1} \tilde{\nabla}_{b}\tilde{\nabla}_{a}\Omega \nonumber \\ 
&& -  \tfrac{1}{2} \tilde{g}^{ba} \tilde{\nabla}_{b}\tilde{\nabla}_{i}f_{ja} -  \tfrac{1}{2} \tilde{g}^{ba} \tilde{\nabla}_{b}\tilde{\nabla}_{j}f_{ia} + 2 \tilde{g}^{ca} \tilde{g}^{db} \tilde{g}_{ij} \Omega^{-1} \tilde{\nabla}_{a}\Omega \tilde{\nabla}_{d}f_{cb} 
\nonumber\\
&& + \tfrac{1}{2} \tilde{g}^{ca} \tilde{g}^{db} \tilde{g}_{ij} \tilde{\nabla}_{d}\tilde{\nabla}_{c}f_{ab}  + 2 \tilde{g}^{ca} \tilde{g}^{db} \tilde{g}_{ij} f_{ab} \Omega^{-1} \tilde{\nabla}_{d}\tilde{\nabla}_{c}\Omega + \tfrac{1}{2} \tilde{\nabla}_{i}\dot{f}_{0}{}_{j} 
\nonumber\\
&& -  \tilde{g}^{ba} \Omega^{-1} \tilde{\nabla}_{a}\Omega \tilde{\nabla}_{i}f_{jb} + \dot{\Omega} \Omega^{-1} \tilde{\nabla}_{i}f_{0}{}_{j} + \tfrac{1}{2} \tilde{\nabla}_{j}\dot{f}_{0}{}_{i} -  \tilde{g}^{ba} \Omega^{-1} \tilde{\nabla}_{a}\Omega \tilde{\nabla}_{j}f_{ib}
\nonumber\\
&&  + \dot{\Omega} \Omega^{-1} \tilde{\nabla}_{j}f_{0}{}_{i} + \tfrac{1}{2} \tilde{\nabla}_{j}\tilde{\nabla}_{i}f,
\label{dg_conf31}
\end{eqnarray}
with dots denoting time derivatives. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Background Equations of Motion}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Before we can use the form of \eqref{dg_conf31}, we note that in geometries with a non-vanishing background $T_{\mu\nu}$, we must first solve the background equations of motion and substitute the solutions for $\rho$ and $p$ in terms of $\Omega(\tau)$ into the fluctuations themselves. Recovering the background solution does not pose the same difficulties as the fluctuations, and thus potentially can all be done non-programmatically. We express here the core results in solving $\Delta_{\mu\nu} = G_{\mu\nu} + T_{\mu\nu} = 0$, including covariant conservation: 
\begin{eqnarray}
ds^2 &=& \Omega^2(\tau)\tilde g_{\mu\nu} dx^\mu dx^\nu,\qquad 
\tilde g_{\mu\nu} = \text{diag}\left(-1,\frac{1}{1-kr^2},r^2,r^2\sin^2\theta\right)
\label{geom}
\\ \nonumber\\
G_{00}&=& -3k - 3 \dot\Omega^2\Omega^{-2}
\qquad
G_{ij} = k\tilde g_{ij} - \dot\Omega^2\Omega^{-2}\tilde g_{ij} + 2\ddot\Omega \Omega^{-1} \tilde g_{ij}
\\ \nonumber\\
T_{\mu\nu} &=& (\rho+p)U_\mu U_\nu + p\Omega^2 \tilde g_{\mu\nu},\qquad U_\mu = - \Omega \delta^0_\mu  
\\ \nonumber\\
\Delta^{(0)}_{00} &=& -3k - 3 \dot\Omega^2\Omega^{-2} + \Omega^2 \rho
\\ \nonumber\\
&\to&\rho = 3k\Omega^{-2}+3\dot\Omega^2 \Omega^{-4}
\label{rho}
\\ \nonumber\\
\Delta^{(0)}_{ij} &=& k\tilde g_{ij} - \dot\Omega^2\Omega^{-2}\tilde g_{ij} + 2\ddot\Omega \Omega^{-1} \tilde g_{ij} + \Omega^2 p
\tilde g_{ij}
\\ \nonumber\\
&\to& p = -k\Omega^{-2} + \dot\Omega^2\Omega^{-4} -2\ddot\Omega \Omega^{-3}
\label{p}
\\ \nonumber\\
\nabla_\mu T^{\mu 0} &=& \Omega^{-5}\left( \tilde g^{ab} T_{ab} \dot{\Omega} + T_{00}{} \dot{\Omega} + \dot{T}_{00}{} \Omega -  \Omega \tilde{\nabla}_{a}T_{0}{}^{a}\right) 
\nonumber\\
&=& 3 \dot{\Omega}  \Omega^{-3}p + 3 \dot{\Omega}  \Omega^{-3}\rho +  \Omega^{-2}\dot{\rho}
\label{Tcons0}
\\ \nonumber\\
\nabla_\mu T^{\mu i} &=& \Omega^{-5}\left(-2 T_{0}{}^{i} \dot{\Omega} -  \dot{T}_{0}{}^{i} \Omega + \Omega \tilde{\nabla}_{a}T^{ia}\right)
\nonumber\\
&=&0.
\end{eqnarray}
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{$\delta G_{\mu\nu}$ and $\delta T_{\mu\nu}$ Fluctuations}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We now perturb the perfect fluid energy momentum tensor and subsequently substitute the background quantities $\rho$ and $p$ which have been given in terms of $\Omega(x)$ above. We also utilize the conformal \eqref{dg_conf31} and initiate the SVT3 decomposition of the $f_{\mu\nu}$, to obtain the entire SVT3 fluctuations for $\delta G_{\mu\nu}$ and $\delta T_{\mu\nu}$:
\begin{eqnarray}
ds^2 &=& \Omega^2(\tau)[\tilde g_{\mu\nu}+ f_{\mu\nu}] dx^\mu dx^\nu
\quad 
\tilde g_{\mu\nu} = \text{diag}\left(-1,\frac{1}{1-kr^2},r^2,r^2\sin^2\theta\right)
\nonumber\\ \\
f_{00} &=& -2\phi,\qquad f_{0i} = \tilde\nabla_i B + B_i,
\nonumber\\
f_{ij} &=& -2\psi \tilde g_{ij} + 2\tilde\nabla_i\tilde\nabla_j E + 
\tilde\nabla_i E_j +\tilde\nabla_j E_i + 2E_{ij}
\label{svt}
\\ \nonumber\\
\delta T_{00}&=& \Omega^2 \delta \rho + (6 k + 6 \dot{\Omega}^2 \Omega^{-2}) \phi 
\\  \nonumber\\ 
\delta T_{0i}&=& (- k + \dot{\Omega}^2 \Omega^{-2} - 2 \overset{..}{\Omega} \Omega^{-1}) \tilde{\nabla}_{i}B \nonumber \\ 
&& + (-4 \dot{\Omega}^2 \Omega^{-3} + 2 \overset{..}{\Omega} \Omega^{-2} - 2 k \Omega^{-1}) \tilde{\nabla}_{i}V+(- k + \dot{\Omega}^2 \Omega^{-2} - 2 \overset{..}{\Omega} \Omega^{-1}) B_{i} \nonumber \\ 
&& + (-4 \dot{\Omega}^2 \Omega^{-3} + 2 \overset{..}{\Omega} \Omega^{-2} - 2 k \Omega^{-1}) V_{i}
\\  \nonumber\\ 
\delta T_{ij}&=& \Omega^2 \delta p \tilde{g}_{ij} + (2 k \tilde{g}_{ij} - 2 \dot{\Omega}^2 \Omega^{-2} \tilde{g}_{ij} + 4 \overset{..}{\Omega} \Omega^{-1} \tilde{g}_{ij}) \psi \\ 
&& + (-2 k + 2 \dot{\Omega}^2 \Omega^{-2} - 4 \overset{..}{\Omega} \Omega^{-1}) \tilde{\nabla}_{i}\tilde{\nabla}_{j}E+(- k + \dot{\Omega}^2 \Omega^{-2} - 2 \overset{..}{\Omega} \Omega^{-1}) \tilde{\nabla}_{i}E_{j} \nonumber \\ 
&& + (- k + \dot{\Omega}^2 \Omega^{-2} - 2 \overset{..}{\Omega} \Omega^{-1}) \tilde{\nabla}_{j}E_{i}+(-2 k + 2 \dot{\Omega}^2 \Omega^{-2} - 4 \overset{..}{\Omega} \Omega^{-1}) E_{ij}
\nonumber\\  \nonumber\\ 
g^{\mu\nu}\delta T_{\mu\nu}&=& 3 \delta p -  \delta \rho + (-6 \dot{\Omega}^2 \Omega^{-4} - 6 k \Omega^{-2}) \phi + (-6 \dot{\Omega}^2 \Omega^{-4} + 12 \overset{..}{\Omega} \Omega^{-3} + 6 k \Omega^{-2}) \psi \nonumber \\ 
&& + (2 \dot{\Omega}^2 \Omega^{-4} - 4 \overset{..}{\Omega} \Omega^{-3} - 2 k \Omega^{-2}) \tilde{\nabla}_{a}\tilde{\nabla}^{a}E
\\ \nonumber\\
\delta G_{00}&=& 6 \dot{\Omega} \Omega^{-1} \dot{\psi} - 6 k \phi - 6 k \psi + 2 \dot{\Omega} \Omega^{-1} \tilde{\nabla}_{a}\tilde{\nabla}^{a}B - 2 \dot{\Omega} \Omega^{-1} \tilde{\nabla}_{a}\tilde{\nabla}^{a}\dot{E} - 2 \tilde{\nabla}_{a}\tilde{\nabla}^{a}\psi 
\nonumber\\  \\ 
\delta G_{0i}&=& (3 k -  \dot{\Omega}^2 \Omega^{-2} + 2 \overset{..}{\Omega} \Omega^{-1}) \tilde{\nabla}_{i}B - 2 k \tilde{\nabla}_{i}\dot{E} - 2 \tilde{\nabla}_{i}\dot{\psi} - 2 \dot{\Omega} \Omega^{-1} \tilde{\nabla}_{i}\phi 
\nonumber\\
&&+(2 k -  \dot{\Omega}^2 \Omega^{-2} + 2 \overset{..}{\Omega} \Omega^{-1}) B_{i} -  k \dot{E}_{i} + \tfrac{1}{2} \tilde{\nabla}_{a}\tilde{\nabla}^{a}B_{i} -  \tfrac{1}{2} \tilde{\nabla}_{a}\tilde{\nabla}^{a}\dot{E}_{i}
\\  \nonumber\\ 
\delta G_{ij}&=& -2 \overset{..}{\psi} \tilde{g}_{ij} - 2 \dot{\Omega} \Omega^{-1} \dot{\phi} \tilde{g}_{ij} - 4 \dot{\Omega} \Omega^{-1} \dot{\psi} \tilde{g}_{ij} + (2 \dot{\Omega}^2 \Omega^{-2} \tilde{g}_{ij} - 4 \overset{..}{\Omega} \Omega^{-1} \tilde{g}_{ij}) \phi \nonumber \\ 
&& + (2 \dot{\Omega}^2 \Omega^{-2} \tilde{g}_{ij} - 4 \overset{..}{\Omega} \Omega^{-1} \tilde{g}_{ij}) \psi - 2 \dot{\Omega} \Omega^{-1} \tilde{g}_{ij} \tilde{\nabla}_{a}\tilde{\nabla}^{a}B -  \tilde{g}_{ij} \tilde{\nabla}_{a}\tilde{\nabla}^{a}\dot{B} 
\nonumber\\
&&+ \tilde{g}_{ij} \tilde{\nabla}_{a}\tilde{\nabla}^{a}\overset{..}{E}  + 2 \dot{\Omega} \Omega^{-1} \tilde{g}_{ij} \tilde{\nabla}_{a}\tilde{\nabla}^{a}\dot{E} -  \tilde{g}_{ij} \tilde{\nabla}_{a}\tilde{\nabla}^{a}\phi + \tilde{g}_{ij} \tilde{\nabla}_{a}\tilde{\nabla}^{a}\psi 
\nonumber\\
&&+ 2 \dot{\Omega} \Omega^{-1} \tilde{\nabla}_{j}\tilde{\nabla}_{i}B + \tilde{\nabla}_{j}\tilde{\nabla}_{i}\dot{B} -  \tilde{\nabla}_{j}\tilde{\nabla}_{i}\overset{..}{E}  - 2 \dot{\Omega} \Omega^{-1} \tilde{\nabla}_{j}\tilde{\nabla}_{i}\dot{E} 
\nonumber\\
&&+ (2 k - 2 \dot{\Omega}^2 \Omega^{-2} + 4 \overset{..}{\Omega} \Omega^{-1}) \tilde{\nabla}_{j}\tilde{\nabla}_{i}E + \tilde{\nabla}_{j}\tilde{\nabla}_{i}\phi -  \tilde{\nabla}_{j}\tilde{\nabla}_{i}\psi +\dot{\Omega} \Omega^{-1} \tilde{\nabla}_{i}B_{j} \nonumber \\ 
&& + \tfrac{1}{2} \tilde{\nabla}_{i}\dot{B}_{j} -  \tfrac{1}{2} \tilde{\nabla}_{i}\overset{..}{E}_{j} -  \dot{\Omega} \Omega^{-1} \tilde{\nabla}_{i}\dot{E}_{j} + (k -  \dot{\Omega}^2 \Omega^{-2} + 2 \overset{..}{\Omega} \Omega^{-1}) \tilde{\nabla}_{i}E_{j} 
\nonumber\\
&&+ \dot{\Omega} \Omega^{-1} \tilde{\nabla}_{j}B_{i} + \tfrac{1}{2} \tilde{\nabla}_{j}\dot{B}_{i} -  \tfrac{1}{2} \tilde{\nabla}_{j}\overset{..}{E}_{i} -  \dot{\Omega} \Omega^{-1} \tilde{\nabla}_{j}\dot{E}_{i} 
\nonumber\\
&&+ (k -  \dot{\Omega}^2 \Omega^{-2} + 2 \overset{..}{\Omega} \Omega^{-1}) \tilde{\nabla}_{j}E_{i}- \overset{..}{E}_{ij} - 2 \dot{\Omega} \Omega^{-1} \dot{E}_{ij} \nonumber \\ 
&& + (-2 \dot{\Omega}^2 \Omega^{-2} + 4 \overset{..}{\Omega} \Omega^{-1}) E_{ij} + \tilde{\nabla}_{a}\tilde{\nabla}^{a}E_{ij}
\\  \nonumber\\ 
g^{\mu\nu}\delta G_{\mu\nu}&=& -6 \Omega^{-2} \overset{..}{\psi} - 6 \dot{\Omega} \Omega^{-3} \dot{\phi} - 18 \dot{\Omega} \Omega^{-3} \dot{\psi} + (6 \dot{\Omega}^2 \Omega^{-4} - 12 \overset{..}{\Omega} \Omega^{-3} + 6 k \Omega^{-2}) \phi \nonumber \\ 
&& + (6 \dot{\Omega}^2 \Omega^{-4} - 12 \overset{..}{\Omega} \Omega^{-3} + 6 k \Omega^{-2}) \psi - 6 \dot{\Omega} \Omega^{-3} \tilde{\nabla}_{a}\tilde{\nabla}^{a}B - 2 \Omega^{-2} \tilde{\nabla}_{a}\tilde{\nabla}^{a}\dot{B} 
\nonumber\\
&&+ 2 \Omega^{-2} \tilde{\nabla}_{a}\tilde{\nabla}^{a}\overset{..}{E}  + 6 \dot{\Omega} \Omega^{-3} \tilde{\nabla}_{a}\tilde{\nabla}^{a}\dot{E} - 2 \Omega^{-2} \tilde{\nabla}_{a}\tilde{\nabla}^{a}\phi + 4 \Omega^{-2} \tilde{\nabla}_{a}\tilde{\nabla}^{a}\psi 
\nonumber\\
&&+ (-2 \dot{\Omega}^2 \Omega^{-4} + 4 \overset{..}{\Omega} \Omega^{-3} + 2 k \Omega^{-2}) \tilde{\nabla}_{a}\tilde{\nabla}^{a}E 
\end{eqnarray}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Field Equations}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Next we add $\delta G_{\mu\nu}$ to $\delta T_{\mu\nu}$ while simplifying common terms to obtain the field equations $\Delta_{\mu\nu} = 0$:
\begin{eqnarray}
\Delta_{\mu\nu}&\equiv&\delta G_{\mu\nu} + \delta T_{\mu\nu}
\\ \nonumber\\
\Delta_{00}&=& \Omega^2 \delta \rho + 6 \dot{\Omega} \Omega^{-1} \dot{\psi} + 6 \dot{\Omega}^2 \Omega^{-2} \phi - 6 k \psi + 2 \dot{\Omega} \Omega^{-1} \tilde{\nabla}_{a}\tilde{\nabla}^{a}B - 2 \dot{\Omega} \Omega^{-1} \tilde{\nabla}_{a}\tilde{\nabla}^{a}\dot{E}
\nonumber\\
&& - 2 \tilde{\nabla}_{a}\tilde{\nabla}^{a}\psi 
\\  \nonumber\\ 
\Delta_{0i}&=& 2 k \tilde{\nabla}_{i}B - 2 k \tilde{\nabla}_{i}\dot{E} - 2 \tilde{\nabla}_{i}\dot{\psi} + (-4 \dot{\Omega}^2 \Omega^{-3} + 2 \overset{..}{\Omega} \Omega^{-2} - 2 k \Omega^{-1}) \tilde{\nabla}_{i}V 
\nonumber\\
&&- 2 \dot{\Omega} \Omega^{-1} \tilde{\nabla}_{i}\phi +k B_{i} -  k \dot{E}_{i} + (-4 \dot{\Omega}^2 \Omega^{-3} + 2 \overset{..}{\Omega} \Omega^{-2} - 2 k \Omega^{-1}) V_{i}
\nonumber\\
&& + \tfrac{1}{2} \tilde{\nabla}_{a}\tilde{\nabla}^{a}B_{i} -  \tfrac{1}{2} \tilde{\nabla}_{a}\tilde{\nabla}^{a}\dot{E}_{i}
\\  \nonumber\\ 
\Delta_{ij}&=& -2 \overset{..}{\psi} \tilde{g}_{ij} + \Omega^2 \delta p \tilde{g}_{ij} - 2 \dot{\Omega} \Omega^{-1} \dot{\phi} \tilde{g}_{ij} - 4 \dot{\Omega} \Omega^{-1} \dot{\psi} \tilde{g}_{ij}  + 2 k \tilde{g}_{ij} \psi \nonumber \\ 
&& + (2 \dot{\Omega}^2 \Omega^{-2} \tilde{g}_{ij} - 4 \overset{..}{\Omega} \Omega^{-1} \tilde{g}_{ij}) \phi- 2 \dot{\Omega} \Omega^{-1} \tilde{g}_{ij} \tilde{\nabla}_{a}\tilde{\nabla}^{a}B -  \tilde{g}_{ij} \tilde{\nabla}_{a}\tilde{\nabla}^{a}\dot{B} 
\nonumber\\
&&+ \tilde{g}_{ij} \tilde{\nabla}_{a}\tilde{\nabla}^{a}\overset{..}{E} + 2 \dot{\Omega} \Omega^{-1} \tilde{g}_{ij} \tilde{\nabla}_{a}\tilde{\nabla}^{a}\dot{E} -  \tilde{g}_{ij} \tilde{\nabla}_{a}\tilde{\nabla}^{a}\phi + \tilde{g}_{ij} \tilde{\nabla}_{a}\tilde{\nabla}^{a}\psi 
\nonumber\\
&&+ (-2 k + 2 \dot{\Omega}^2 \Omega^{-2} - 4 \overset{..}{\Omega} \Omega^{-1}) \tilde{\nabla}_{i}\tilde{\nabla}_{j}E + 2 \dot{\Omega} \Omega^{-1} \tilde{\nabla}_{j}\tilde{\nabla}_{i}B + \tilde{\nabla}_{j}\tilde{\nabla}_{i}\dot{B} 
\nonumber\\
&&-  \tilde{\nabla}_{j}\tilde{\nabla}_{i}\overset{..}{E} - 2 \dot{\Omega} \Omega^{-1} \tilde{\nabla}_{j}\tilde{\nabla}_{i}\dot{E} + (2 k - 2 \dot{\Omega}^2 \Omega^{-2} + 4 \overset{..}{\Omega} \Omega^{-1}) \tilde{\nabla}_{j}\tilde{\nabla}_{i}E 
\nonumber\\
&&+ \tilde{\nabla}_{j}\tilde{\nabla}_{i}\phi -  \tilde{\nabla}_{j}\tilde{\nabla}_{i}\psi +\dot{\Omega} \Omega^{-1} \tilde{\nabla}_{i}B_{j}  + \tfrac{1}{2} \tilde{\nabla}_{i}\dot{B}_{j} -  \tfrac{1}{2} \tilde{\nabla}_{i}\overset{..}{E}_{j} -  \dot{\Omega} \Omega^{-1} \tilde{\nabla}_{i}\dot{E}_{j} 
\nonumber\\
&&+ \dot{\Omega} \Omega^{-1} \tilde{\nabla}_{j}B_{i} + \tfrac{1}{2} \tilde{\nabla}_{j}\dot{B}_{i} -  \tfrac{1}{2} \tilde{\nabla}_{j}\overset{..}{E}_{i} -  \dot{\Omega} \Omega^{-1} \tilde{\nabla}_{j}\dot{E}_{i}- \overset{..}{E}_{ij}  - 2 \dot{\Omega} \Omega^{-1} \dot{E}_{ij} 
\nonumber\\
&&- 2 k E_{ij} + \tilde{\nabla}_{a}\tilde{\nabla}^{a}E_{ij}
\\  \nonumber\\ 
g^{\mu\nu}\Delta_{\mu\nu}&=& -6 \Omega^{-2} \overset{..}{\psi} + 3 \delta p -  \delta \rho - 6 \dot{\Omega} \Omega^{-3} \dot{\phi} - 18 \dot{\Omega} \Omega^{-3} \dot{\psi} - 12 \overset{..}{\Omega} \Omega^{-3} \phi + 12 k \Omega^{-2} \psi 
\nonumber\\
&&- 6 \dot{\Omega} \Omega^{-3} \tilde{\nabla}_{a}\tilde{\nabla}^{a}B  - 2 \Omega^{-2} \tilde{\nabla}_{a}\tilde{\nabla}^{a}\dot{B} + 2 \Omega^{-2} \tilde{\nabla}_{a}\tilde{\nabla}^{a}\overset{..}{E} 
\nonumber\\
&&+ 6 \dot{\Omega} \Omega^{-3} \tilde{\nabla}_{a}\tilde{\nabla}^{a}\dot{E} - 2 \Omega^{-2} \tilde{\nabla}_{a}\tilde{\nabla}^{a}\phi + 4 \Omega^{-2} \tilde{\nabla}_{a}\tilde{\nabla}^{a}\psi .
\end{eqnarray}
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Field Equations (Gauge Invariant Form)}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Finally, we form the set of 10 gauge invariants and express the field equations entirely terms of them. While straightforward in theory, in practice one must take special care in the order in which one substitutes the gauge invariants; otherwise, the remaining fluctuations will be expressed in a different basis of gauge invariants than desired.
\begin{eqnarray}
\alpha  &=& \phi + \psi + \dot B - \ddot E,\quad \gamma = - \dot\Omega^{-1}\Omega \psi + B - \dot E,
\quad B_i - \dot E_i,\quad E_{ij},\quad V_i
\nonumber\\ \\
V^{GI} &=& V-\Omega^2 \dot \Omega^{-1}\psi
\\ \nonumber\\
\delta \rho^{GI}&=&\delta \rho - 12 \dot{\Omega}^2 \psi \Omega^{-4} + 6 \overset{..}{\Omega} \psi \Omega^{-3} - 6 k \psi \Omega^{-2}
\\ \nonumber\\ 
\delta p^{GI}&=&\delta p - 4 \dot{\Omega}^2 \psi \Omega^{-4} + 8 \overset{..}{\Omega} \psi \Omega^{-3} + 2 k \psi \Omega^{-2} - 2 \overset{...}{\Omega} \dot{\Omega}^{-1} \psi \Omega^{-2}
\\ \nonumber\\
\Delta_{00}&=& \Omega^2 \delta \rho^{GI}{} - 6 \dot{\Omega}^2 \Omega^{-2} \dot{\gamma} + 6 \dot{\Omega}^2 \Omega^{-2} \alpha + 2 \dot{\Omega} \Omega^{-1} \tilde{\nabla}_{a}\tilde{\nabla}^{a}\gamma 
\\  \nonumber\\ 
\Delta_{0i}&=& 2 \dot{\Omega} \Omega^{-1} \tilde{\nabla}_{i}\dot{\gamma} - 2 \dot{\Omega} \Omega^{-1} \tilde{\nabla}_{i}\alpha + 2 k \tilde{\nabla}_{i}\gamma +k Q_{i} 
\nonumber\\
&&+ (-4 \dot{\Omega}^2 \Omega^{-3} + 2 \overset{..}{\Omega} \Omega^{-2} - 2 k \Omega^{-1}) V_{i} + \tfrac{1}{2} \tilde{\nabla}_{a}\tilde{\nabla}^{a}Q_{i} \nonumber \\ 
&& + (-4 \dot{\Omega}^2 \Omega^{-3} + 2 \overset{..}{\Omega} \Omega^{-2} - 2 k \Omega^{-1}) \tilde{\nabla}_{i}V^{GI}{}
\\  \nonumber\\ 
\Delta_{ij}&=& 2 \dot{\Omega} \Omega^{-1} \overset{..}{\gamma} \tilde{g}_{ij} + \Omega^2 \delta p^{GI}{} \tilde{g}_{ij} - 2 \dot{\Omega} \Omega^{-1} \dot{\alpha} \tilde{g}_{ij} + \dot{\gamma} (-2 \dot{\Omega}^2 \Omega^{-2} \tilde{g}_{ij} + 4 \overset{..}{\Omega} \Omega^{-1} \tilde{g}_{ij}) \nonumber \\ 
&& + (2 \dot{\Omega}^2 \Omega^{-2} \tilde{g}_{ij} - 4 \overset{..}{\Omega} \Omega^{-1} \tilde{g}_{ij}) \alpha -  \tilde{g}_{ij} \tilde{\nabla}_{a}\tilde{\nabla}^{a}\alpha - 2 \dot{\Omega} \Omega^{-1} \tilde{g}_{ij} \tilde{\nabla}_{a}\tilde{\nabla}^{a}\gamma + \tilde{\nabla}_{j}\tilde{\nabla}_{i}\alpha \nonumber \\ 
&& + 2 \dot{\Omega} \Omega^{-1} \tilde{\nabla}_{j}\tilde{\nabla}_{i}\gamma +\tfrac{1}{2} \tilde{\nabla}_{i}\dot{Q}_{j} + \dot{\Omega} \Omega^{-1} \tilde{\nabla}_{i}Q_{j} + \tfrac{1}{2} \tilde{\nabla}_{j}\dot{Q}_{i} + \dot{\Omega} \Omega^{-1} \tilde{\nabla}_{j}Q_{i}- \overset{..}{E}_{ij} 
\nonumber\\
&&- 2 \dot{\Omega} \Omega^{-1} \dot{E}_{ij} - 2 k E_{ij} + \tilde{\nabla}_{a}\tilde{\nabla}^{a}E_{ij}
\\  \nonumber\\ 
g^{\mu\nu}\Delta_{\mu\nu}&=& 6 \dot{\Omega} \Omega^{-3} \overset{..}{\gamma} + 3 \delta p^{GI}{} -  \delta \rho^{GI}{} - 6 \dot{\Omega} \Omega^{-3} \dot{\alpha} + 12 \overset{..}{\Omega} \Omega^{-3} \dot{\gamma} - 12 \overset{..}{\Omega} \Omega^{-3} \alpha 
\nonumber\\
&&- 2 \Omega^{-2} \tilde{\nabla}_{a}\tilde{\nabla}^{a}\alpha  - 6 \dot{\Omega} \Omega^{-3} \tilde{\nabla}_{a}\tilde{\nabla}^{a}\gamma 
\end{eqnarray}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Conservation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
While the ability to express the entire field equations solely in terms of gauge invariants quantities serves as a good check on the accuracy of the calculation, one should also check the conditions of covariant conservation. Here, we note that one cannot simply apply the covariant derivative to the perturbation viz. $\tilde\nabla_\mu \delta T^{\mu\nu}$ since the background geometry is not flat. Rather, one must perturb the entire $\delta (\nabla_\mu T^{\mu\nu})$. Calculating the conservation conditions, we obtain:
\begin{eqnarray}
\delta(\nabla_\mu T^{\mu 0})&=& \delta T^{a}{}_{a} \dot{\Omega} \Omega^{-5} + \delta T_{00}{} \dot{\Omega} \Omega^{-5} -  T^{ab} \dot{\Omega} f_{ab} \Omega^{-5} + T^{a}{}_{a} \dot{\Omega} f_{00}{} \Omega^{-5} 
\nonumber\\
&&+ 2 T_{00}{} \dot{\Omega} f_{00}{} \Omega^{-5} - 2 T_{0}{}^{a} \dot{\Omega} f_{0}{}_{a} \Omega^{-5}  + \dot{\delta T}_{00}{} \Omega^{-4} + \tfrac{1}{2} T^{ab} \dot{f}_{ab} \Omega^{-4} 
\nonumber\\
&&+ \tfrac{3}{2} T_{00}{} \dot{f}_{00}{} \Omega^{-4} - 2 T_{0}{}^{a} \dot{f}_{0}{}_{a} \Omega^{-4} + \tfrac{1}{2} T_{00}{} \dot{f} \Omega^{-4} + 2 \dot{T}_{00}{} f_{00}{} \Omega^{-4} \nonumber \\ 
&& - 2 \dot{T}_{0}{}^{a} f_{0}{}_{a} \Omega^{-4} -  \Omega^{-4} \tilde{\nabla}_{a}\delta T_{0}{}^{a} -  f_{0}{}^{a} \Omega^{-4} \tilde{\nabla}_{a}T_{00}{} -  f_{00}{} \Omega^{-4} \tilde{\nabla}_{a}T_{0}{}^{a}
\nonumber\\
&& -  T_{00}{} \Omega^{-4} \tilde{\nabla}_{a}f_{0}{}^{a}  -  \tfrac{1}{2} T_{0}{}^{a} \Omega^{-4} \tilde{\nabla}_{a}f + f_{0}{}^{a} \Omega^{-4} \tilde{\nabla}_{b}T_{a}{}^{b} + T_{0}{}^{a} \Omega^{-4} \tilde{\nabla}_{b}f_{a}{}^{b} 
\nonumber\\
&&+ f_{ab} \Omega^{-4} \tilde{\nabla}^{b}T_{0}{}^{a}
\\ \nonumber\\
&=& \Omega^{-2} \dot{\delta \rho} + 3 \dot{\Omega} \Omega^{-3} \delta p + 3 \dot{\Omega} \Omega^{-3} \delta \rho 
\nonumber\\
&&+ (-12 \dot{\Omega}^2 \Omega^{-6} + 6 \overset{..}{\Omega} \Omega^{-5} - 6 k \Omega^{-4}) \dot{\psi} \nonumber \\ 
&& + (-4 \dot{\Omega}^2 \Omega^{-6} + 2 \overset{..}{\Omega} \Omega^{-5} - 2 k \Omega^{-4}) \tilde{\nabla}_{a}\tilde{\nabla}^{a}B 
\nonumber\\
&&+ (4 \dot{\Omega}^2 \Omega^{-6} - 2 \overset{..}{\Omega} \Omega^{-5} + 2 k \Omega^{-4}) \tilde{\nabla}_{a}\tilde{\nabla}^{a}\dot{E} \nonumber \\ 
&& + (4 \dot{\Omega}^2 \Omega^{-7} - 2 \overset{..}{\Omega} \Omega^{-6} + 2 k \Omega^{-5}) \tilde{\nabla}_{a}\tilde{\nabla}^{a}V
\\  \nonumber\\ 
&=& \Omega^{-2} \dot{\delta \rho}^{GI}{} + 3 \dot{\Omega} \Omega^{-3} \delta p^{GI}{} + 3 \dot{\Omega} \Omega^{-3} \delta \rho^{GI}{} \nonumber \\ 
&& + (-4 \dot{\Omega}^2 \Omega^{-6} + 2 \overset{..}{\Omega} \Omega^{-5} - 2 k \Omega^{-4}) \tilde{\nabla}_{a}\tilde{\nabla}^{a}\gamma 
\nonumber\\
&&+(4 \dot{\Omega}^2 \Omega^{-7} - 2 \overset{..}{\Omega} \Omega^{-6} + 2 k \Omega^{-5}) \tilde{\nabla}_{a}\tilde{\nabla}^{a}V^{GI}{}
\\ \nonumber\\
\delta(\nabla_\mu T^{\mu i})&=& -2 \delta T_{0}{}^{i} \dot{\Omega} \Omega^{-5} + 2 T_{0}{}^{a} \dot{\Omega} f^{i}{}_{a} \Omega^{-5} - 2 T_{0}{}^{i} \dot{\Omega} f_{00}{} \Omega^{-5} + 2 T^{i}{}_{a} \dot{\Omega} f_{0}{}^{a} \Omega^{-5} 
\nonumber\\
&&-  T^{a}{}_{a} \dot{\Omega} f_{0}{}^{i} \Omega^{-5}  -  T_{00}{} \dot{\Omega} f_{0}{}^{i} \Omega^{-5} -  \dot{\delta T}_{0}{}^{i} \Omega^{-4} -  T_{0}{}^{i} \dot{f}_{00}{} \Omega^{-4} 
\nonumber\\
&&+ T^{i}{}_{a} \dot{f}_{0}{}^{a} \Omega^{-4} 
-  \tfrac{1}{2} T_{0}{}^{i} \dot{f} \Omega^{-4} + \dot{T}_{0}{}^{a} f^{i}{}_{a} \Omega^{-4} -  \dot{T}_{0}{}^{i} f_{00}{} \Omega^{-4} + \dot{T}^{i}{}_{a} f_{0}{}^{a} \Omega^{-4} 
\nonumber\\
&&-  \dot{T}_{00}{} f_{0}{}^{i} \Omega^{-4}
+ \Omega^{-4} \tilde{\nabla}_{a}\delta T^{ia} + f_{0}{}^{i} \Omega^{-4} \tilde{\nabla}_{a}T_{0}{}^{a} + f_{0}{}^{a} \Omega^{-4} \tilde{\nabla}_{a}T_{0}{}^{i}  
\nonumber\\
&&+ T_{0}{}^{i} \Omega^{-4} \tilde{\nabla}_{a}f_{0}{}^{a} 
+ \tfrac{1}{2} T^{i}{}_{a} \Omega^{-4} \tilde{\nabla}^{a}f -  f^{ia} \Omega^{-4} \tilde{\nabla}_{b}T_{a}{}^{b} -  f^{ab} \Omega^{-4} \tilde{\nabla}_{b}T^{i}{}_{a} 
\nonumber\\
&&-  T^{ia} \Omega^{-4} \tilde{\nabla}_{b}f_{a}{}^{b}-  \tfrac{1}{2} T^{ab} \Omega^{-4} \tilde{\nabla}^{i}f_{ab} -  \tfrac{1}{2} T_{00}{} \Omega^{-4} \tilde{\nabla}^{i}f_{00}{} 
\nonumber\\
&&+ T_{0}{}^{a} \Omega^{-4} \tilde{\nabla}^{i}f_{0}{}_{a}
\\  \nonumber\\ 
&=& \Omega^{-2} \tilde{\nabla}^{i}\delta p + (4 \dot{\Omega}^2 \Omega^{-7} - 2 \overset{..}{\Omega} \Omega^{-6} + 2 k \Omega^{-5}) \tilde{\nabla}^{i}\dot{V} \nonumber \\ 
&& + (-4 \dot{\Omega}^3 \Omega^{-8} + 8 \overset{..}{\Omega} \dot{\Omega} \Omega^{-7} - 2 \overset{...}{\Omega} \Omega^{-6} + 2 \dot{\Omega} k \Omega^{-6}) \tilde{\nabla}^{i}V \nonumber \\ 
&& + (4 \dot{\Omega}^2 \Omega^{-6} - 2 \overset{..}{\Omega} \Omega^{-5} + 2 k \Omega^{-4}) \tilde{\nabla}^{i}\phi 
\nonumber\\
&&+(4 \dot{\Omega}^2 \Omega^{-7} - 2 \overset{..}{\Omega} \Omega^{-6} + 2 k \Omega^{-5}) \dot{V}^{i} \nonumber \\ 
&& + (-4 \dot{\Omega}^3 \Omega^{-8} + 8 \overset{..}{\Omega} \dot{\Omega} \Omega^{-7} - 2 \overset{...}{\Omega} \Omega^{-6} + 2 \dot{\Omega} k \Omega^{-6}) V^{i}
\\  \nonumber\\ 
&=& \Omega^{-2} \tilde{\nabla}^{i}\delta p^{GI}{} + (-4 \dot{\Omega}^2 \Omega^{-6} + 2 \overset{..}{\Omega} \Omega^{-5} - 2 k \Omega^{-4}) \tilde{\nabla}^{i}\dot{\gamma} \nonumber \\ 
&& + (4 \dot{\Omega}^2 \Omega^{-6} - 2 \overset{..}{\Omega} \Omega^{-5} + 2 k \Omega^{-4}) \tilde{\nabla}^{i}\alpha 
\nonumber\\
&&+(4 \dot{\Omega}^2 \Omega^{-7} - 2 \overset{..}{\Omega} \Omega^{-6} + 2 k \Omega^{-5}) \dot{V}^{i} \nonumber \\ 
&& + (-4 \dot{\Omega}^3 \Omega^{-8} + 8 \overset{..}{\Omega} \dot{\Omega} \Omega^{-7} - 2 \overset{...}{\Omega} \Omega^{-6} + 2 \dot{\Omega} k \Omega^{-6}) V^{i} 
\nonumber\\
&&+ (4 \dot{\Omega}^2 \Omega^{-7} - 2 \overset{..}{\Omega} \Omega^{-6} + 2 k \Omega^{-5}) \tilde{\nabla}^{i}\dot{V}^{GI}{} \nonumber \\ 
&& + (-4 \dot{\Omega}^3 \Omega^{-8} + 8 \overset{..}{\Omega} \dot{\Omega} \Omega^{-7} - 2 \overset{...}{\Omega} \Omega^{-6} + 2 \dot{\Omega} k \Omega^{-6}) \tilde{\nabla}^{i}V^{GI}{}
\\ \nonumber\\
\delta(\nabla_\mu G^{\mu 0})&=& \delta G^{a}{}_{a} \dot{\Omega} \Omega^{-5} + \delta G_{00}{} \dot{\Omega} \Omega^{-5} - 2 B^{a} G_{0}{}_{a} \dot{\Omega} \Omega^{-5} - 2 G^{ab} \dot{\Omega} E_{ab} \Omega^{-5} 
\nonumber\\
&&- 2 G^{a}{}_{a} \dot{\Omega} \phi \Omega^{-5} - 4 G_{00}{} \dot{\Omega} \phi \Omega^{-5}+ 2 G^{a}{}_{a} \dot{\Omega} \psi \Omega^{-5} + \dot{\delta G}_{00}{} \Omega^{-4} 
\nonumber\\
&&- 2 B^{a} \dot{G}_{0}{}_{a} \Omega^{-4} - 2 \dot{B}^{a} G_{0}{}_{a} \Omega^{-4} + G^{ab} \dot{E}_{ab} \Omega^{-4} - 2 G_{00}{} \dot{\phi} \Omega^{-4} \nonumber \\ 
&& -  G^{a}{}_{a} \dot{\psi} \Omega^{-4} - 3 G_{00}{} \dot{\psi} \Omega^{-4} + 2 k G_{0}{}^{a} E_{a} \Omega^{-4} - 4 \dot{G}_{00}{} \phi \Omega^{-4} 
\nonumber\\
&&- 2 G_{0}{}^{a} \dot{\Omega} \Omega^{-5} \tilde{\nabla}_{a}B - 2 \dot{G}_{0}{}^{a} \Omega^{-4} \tilde{\nabla}_{a}B - 2 G_{0}{}^{a} \Omega^{-4} \tilde{\nabla}_{a}\dot{B} 
\nonumber\\
&&-  \Omega^{-4} \tilde{\nabla}_{a}\delta G_{0}{}^{a} 
-  B^{a} \Omega^{-4} \tilde{\nabla}_{a}G_{00}{} + 2 \phi \Omega^{-4} \tilde{\nabla}_{a}G_{0}{}^{a} - 2 \psi \Omega^{-4} \tilde{\nabla}_{a}G_{0}{}^{a} \nonumber \\ 
&& + 2 k G_{0}{}^{a} \Omega^{-4} \tilde{\nabla}_{a}E -  G_{0}{}^{a} \Omega^{-4} \tilde{\nabla}_{a}\phi + G_{0}{}^{a} \Omega^{-4} \tilde{\nabla}_{a}\psi 
\nonumber\\
&&
-  G_{00}{} \Omega^{-4} \tilde{\nabla}_{a}\tilde{\nabla}^{a}B 
+ G_{00}{} \Omega^{-4} \tilde{\nabla}_{a}\tilde{\nabla}^{a}\dot{E}  
-  \Omega^{-4} \tilde{\nabla}_{a}G_{00}{} \tilde{\nabla}^{a}B 
\nonumber\\
&&+ B^{a} \Omega^{-4} \tilde{\nabla}_{b}G_{a}{}^{b} 
+ \Omega^{-4} \tilde{\nabla}^{a}B \tilde{\nabla}_{b}G_{a}{}^{b} + G_{0}{}^{a} \Omega^{-4} \tilde{\nabla}_{b}\tilde{\nabla}^{b}E_{a}  
\nonumber\\
&&+ G_{0}{}^{a} \Omega^{-4} \tilde{\nabla}_{b}\tilde{\nabla}^{b}\tilde{\nabla}_{a}E 
+ 2 E_{ab} \Omega^{-4} \tilde{\nabla}^{b}G_{0}{}^{a} + \Omega^{-4} \tilde{\nabla}_{a}E_{b} \tilde{\nabla}^{b}G_{0}{}^{a}
\nonumber\\
&& + \Omega^{-4} \tilde{\nabla}_{b}E_{a} \tilde{\nabla}^{b}G_{0}{}^{a}  + 2 \Omega^{-4} \tilde{\nabla}_{b}\tilde{\nabla}_{a}E \tilde{\nabla}^{b}G_{0}{}^{a} + G_{ab} \Omega^{-4} \tilde{\nabla}^{b}\dot{E}^{a} 
\nonumber\\
&&- 2 G_{ab} \dot{\Omega} \Omega^{-5} \tilde{\nabla}^{b}E^{a} 
+ G_{ab} \Omega^{-4} \tilde{\nabla}^{b}\tilde{\nabla}^{a}\dot{E} - 2 G_{ab} \dot{\Omega} \Omega^{-5} \tilde{\nabla}^{b}\tilde{\nabla}^{a}E
\nonumber\\  \nonumber\\ 
&=&0
\\  \nonumber\\ 
\delta(\nabla_\mu G^{\mu i})&=& -2 \delta G_{0}{}^{i} \dot{\Omega} \Omega^{-5} -  B^{i} G^{a}{}_{a} \dot{\Omega} \Omega^{-5} + 2 B^{a} G^{i}{}_{a} \dot{\Omega} \Omega^{-5} -  B^{i} G_{00}{} \dot{\Omega} \Omega^{-5} 
\nonumber\\
&&+ 4 G_{0}{}^{a} \dot{\Omega} E^{i}{}_{a} \Omega^{-5} + 4 G_{0}{}^{i} \dot{\Omega} \phi \Omega^{-5} - 4 G_{0}{}^{i} \dot{\Omega} \psi \Omega^{-5} -  \dot{\delta G}_{0}{}^{i} \Omega^{-4} 
\nonumber\\
&&+ B^{a} \dot{G}^{i}{}_{a} \Omega^{-4} -  B^{i} \dot{G}_{00}{} \Omega^{-4} + \dot{B}^{a} G^{i}{}_{a} \Omega^{-4}+ G_{0}{}^{i} \dot{\phi} \Omega^{-4} + 3 G_{0}{}^{i} \dot{\psi} \Omega^{-4}
\nonumber\\
&& + 2 \dot{G}_{0}{}^{a} E^{i}{}_{a} \Omega^{-4} - 2 k G^{i}{}_{a} E^{a} \Omega^{-4} + 2 \dot{G}_{0}{}^{i} \phi \Omega^{-4} - 2 \dot{G}_{0}{}^{i} \psi \Omega^{-4}  
\nonumber\\
&&+ \Omega^{-4} \tilde{\nabla}_{a}\delta G^{ia} + 4 \psi \Omega^{-4} \tilde{\nabla}_{a}G^{ia} + B^{i} \Omega^{-4} \tilde{\nabla}_{a}G_{0}{}^{a} + B^{a} \Omega^{-4} \tilde{\nabla}_{a}G_{0}{}^{i} 
\nonumber\\
&&+ 2 G_{0}{}^{a} \dot{\Omega} \Omega^{-5} \tilde{\nabla}_{a}E^{i} + \dot{G}_{0}{}^{a} \Omega^{-4} \tilde{\nabla}_{a}E^{i} + G_{0}{}^{i} \Omega^{-4} \tilde{\nabla}_{a}\tilde{\nabla}^{a}B 
\nonumber\\
&&-  G_{0}{}^{i} \Omega^{-4} \tilde{\nabla}_{a}\tilde{\nabla}^{a}\dot{E} + 2 G^{i}{}_{a} \dot{\Omega} \Omega^{-5} \tilde{\nabla}^{a}B + \dot{G}^{i}{}_{a} \Omega^{-4} \tilde{\nabla}^{a}B \nonumber \\ 
&& + \Omega^{-4} \tilde{\nabla}_{a}G_{0}{}^{i} \tilde{\nabla}^{a}B + G^{i}{}_{a} \Omega^{-4} \tilde{\nabla}^{a}\dot{B} - 2 k G^{i}{}_{a} \Omega^{-4} \tilde{\nabla}^{a}E 
\nonumber\\
&&+ G^{i}{}_{a} \Omega^{-4} \tilde{\nabla}^{a}\phi 
-  G^{i}{}_{a} \Omega^{-4} \tilde{\nabla}^{a}\psi - 2 E^{ia} \Omega^{-4} \tilde{\nabla}_{b}G_{a}{}^{b} 
\nonumber\\
&&-  \Omega^{-4} \tilde{\nabla}^{a}E^{i} \tilde{\nabla}_{b}G_{a}{}^{b} 
- 2 E^{ab} \Omega^{-4} \tilde{\nabla}_{b}G^{i}{}_{a} -  G^{i}{}_{a} \Omega^{-4} \tilde{\nabla}_{b}\tilde{\nabla}^{b}E^{a}  
\nonumber\\
&&-  G^{i}{}_{a} \Omega^{-4} \tilde{\nabla}_{b}\tilde{\nabla}^{b}\tilde{\nabla}^{a}E 
-  \Omega^{-4} \tilde{\nabla}_{a}G^{i}{}_{b} \tilde{\nabla}^{b}E^{a} -  \Omega^{-4} \tilde{\nabla}_{b}G^{i}{}_{a} \tilde{\nabla}^{b}E^{a} 
\nonumber\\
&&- 2 \Omega^{-4} \tilde{\nabla}_{b}G^{i}{}_{a} \tilde{\nabla}^{b}\tilde{\nabla}^{a}E  -  G^{a}{}_{a} \dot{\Omega} \Omega^{-5} \tilde{\nabla}^{i}B -  G_{00}{} \dot{\Omega} \Omega^{-5} \tilde{\nabla}^{i}B 
\nonumber\\
&&-  \dot{G}_{00}{} \Omega^{-4} \tilde{\nabla}^{i}B 
+ \Omega^{-4} \tilde{\nabla}_{a}G_{0}{}^{a} \tilde{\nabla}^{i}B + G_{0}{}^{a} \Omega^{-4} \tilde{\nabla}^{i}B_{a} 
\nonumber\\
&&-  G^{ab} \Omega^{-4} \tilde{\nabla}^{i}E_{ab} 
+ 2 G_{0}{}^{a} \dot{\Omega} \Omega^{-5} \tilde{\nabla}^{i}E_{a} + \dot{G}_{0}{}^{a} \Omega^{-4} \tilde{\nabla}^{i}E_{a} 
\nonumber\\
&&-  \Omega^{-4} \tilde{\nabla}_{b}G_{a}{}^{b} \tilde{\nabla}^{i}E^{a} 
+ G_{00}{} \Omega^{-4} \tilde{\nabla}^{i}\phi  + G^{a}{}_{a} \Omega^{-4} \tilde{\nabla}^{i}\psi 
\nonumber\\
&&+ G_{0}{}^{a} \Omega^{-4} \tilde{\nabla}^{i}\tilde{\nabla}_{a}B + 4 G_{0}{}^{a} \dot{\Omega} \Omega^{-5} \tilde{\nabla}^{i}\tilde{\nabla}_{a}E 
+ 2 \dot{G}_{0}{}^{a} \Omega^{-4} \tilde{\nabla}^{i}\tilde{\nabla}_{a}E
\nonumber\\
&& - 2 \Omega^{-4} \tilde{\nabla}_{b}G_{a}{}^{b} \tilde{\nabla}^{i}\tilde{\nabla}^{a}E -  G_{ab} \Omega^{-4} \tilde{\nabla}^{i}\tilde{\nabla}^{b}E^{a} 
-  G_{ab} \Omega^{-4} \tilde{\nabla}^{i}\tilde{\nabla}^{b}\tilde{\nabla}^{a}E
\nonumber\\  \nonumber\\ 
&=&0
\\ \nonumber\\
\delta(\nabla_\mu \Delta^{\mu 0})&=& \Omega^{-2} \dot{\delta \rho}^{GI}{} + 3 \dot{\Omega} \Omega^{-3} \delta p^{GI}{} + 3 \dot{\Omega} \Omega^{-3} \delta \rho^{GI}{} \nonumber \\ 
&& + (-4 \dot{\Omega}^2 \Omega^{-6} + 2 \overset{..}{\Omega} \Omega^{-5} - 2 k \Omega^{-4}) \tilde{\nabla}_{a}\tilde{\nabla}^{a}\gamma 
\nonumber\\
&&+(4 \dot{\Omega}^2 \Omega^{-7} - 2 \overset{..}{\Omega} \Omega^{-6} + 2 k \Omega^{-5}) \tilde{\nabla}_{a}\tilde{\nabla}^{a}V^{GI}{}
\\  \nonumber\\ 
\delta(\nabla_\mu \Delta^{\mu i})&=& \Omega^{-2} \tilde{\nabla}^{i}\delta p^{GI}{} + (-4 \dot{\Omega}^2 \Omega^{-6} + 2 \overset{..}{\Omega} \Omega^{-5} - 2 k \Omega^{-4}) \tilde{\nabla}^{i}\dot{\gamma} \nonumber \\ 
&& + (4 \dot{\Omega}^2 \Omega^{-6} - 2 \overset{..}{\Omega} \Omega^{-5} + 2 k \Omega^{-4}) \tilde{\nabla}^{i}\alpha 
\nonumber\\
&&+(4 \dot{\Omega}^2 \Omega^{-7} - 2 \overset{..}{\Omega} \Omega^{-6} + 2 k \Omega^{-5}) \dot{V}^{i} \nonumber \\ 
&& + (-4 \dot{\Omega}^3 \Omega^{-8} + 8 \overset{..}{\Omega} \dot{\Omega} \Omega^{-7} - 2 \overset{...}{\Omega} \Omega^{-6} + 2 \dot{\Omega} k \Omega^{-6}) V^{i} 
\nonumber\\
&&+ (4 \dot{\Omega}^2 \Omega^{-7} - 2 \overset{..}{\Omega} \Omega^{-6} + 2 k \Omega^{-5}) \tilde{\nabla}^{i}\dot{V}^{GI}{} \nonumber \\ 
&& + (-4 \dot{\Omega}^3 \Omega^{-8} + 8 \overset{..}{\Omega} \dot{\Omega} \Omega^{-7} - 2 \overset{...}{\Omega} \Omega^{-6} + 2 \dot{\Omega} k \Omega^{-6}) \tilde{\nabla}^{i}V^{GI}{}
\\  \nonumber\\ 
\nabla_i \delta(\nabla_\mu \Delta^{\mu i})&=& \Omega^{-2} \tilde{\nabla}_{a}\tilde{\nabla}^{a}\delta p^{GI}{} + (-4 \dot{\Omega}^2 \Omega^{-6} + 2 \overset{..}{\Omega} \Omega^{-5} - 2 k \Omega^{-4}) \tilde{\nabla}_{a}\tilde{\nabla}^{a}\dot{\gamma} \nonumber \\ 
&& + (4 \dot{\Omega}^2 \Omega^{-6} - 2 \overset{..}{\Omega} \Omega^{-5} + 2 k \Omega^{-4}) \tilde{\nabla}_{a}\tilde{\nabla}^{a}\alpha 
\nonumber\\
&&+(4 \dot{\Omega}^2 \Omega^{-7} - 2 \overset{..}{\Omega} \Omega^{-6} + 2 k \Omega^{-5}) \tilde{\nabla}_{a}\tilde{\nabla}^{a}\dot{V}^{GI}{} \nonumber \\ 
&& + (-4 \dot{\Omega}^3 \Omega^{-8} + 8 \overset{..}{\Omega} \dot{\Omega} \Omega^{-7} - 2 \overset{...}{\Omega} \Omega^{-6} + 2 \dot{\Omega} k \Omega^{-6}) \tilde{\nabla}_{a}\tilde{\nabla}^{a}V^{GI}{}
\end{eqnarray}
Confirming our calculations, we find that $\delta(\nabla_\mu G^{\mu \nu})$ evaluates to zero as expected from the Bianchi identity and $\delta(\nabla_\mu \Delta^{\mu \nu})=\delta(\nabla_\mu T^{\mu \nu})$. The above thus serves to define the perturbed covariant conservation condition for a RW perfect fluid.
%
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Higher Derivative Relations}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In order to assess the status of the decomposition theorem, one lastly needs to apply higher derivatives to the field equations. With the background 3-space geometry having constant spatial curvature, we programatically perform a series of covariant derivative commutations to bring the higher-derivative equations in as simplified form as possible.
\begin{eqnarray}
\tilde\nabla^i\Delta_{0i}&=& 2 \dot{\Omega} \Omega^{-1} \tilde{\nabla}_{a}\tilde{\nabla}^{a}\dot{\gamma} - 2 \dot{\Omega} \Omega^{-1} \tilde{\nabla}_{a}\tilde{\nabla}^{a}\alpha + 2 k \tilde{\nabla}_{a}\tilde{\nabla}^{a}\gamma 
\nonumber\\
&&+(-4 \dot{\Omega}^2 \Omega^{-3} + 2 \overset{..}{\Omega} \Omega^{-2} - 2 k \Omega^{-1}) \tilde{\nabla}_{a}\tilde{\nabla}^{a}V^{GI}{}
\\  \nonumber\\ 
\tilde g^{ij}\Delta_{ij}&=& 6 \dot{\Omega} \Omega^{-1} \overset{..}{\gamma} + 3 \Omega^2 \delta p^{GI}{} - 6 \dot{\Omega} \Omega^{-1} \dot{\alpha} 
\nonumber\\
&&+ (-6 \dot{\Omega}^2 \Omega^{-2} + 12 \overset{..}{\Omega} \Omega^{-1}) \dot{\gamma} + (6 \dot{\Omega}^2 \Omega^{-2} - 12 \overset{..}{\Omega} \Omega^{-1}) \alpha \nonumber \\ 
&& - 2 \tilde{\nabla}_{a}\tilde{\nabla}^{a}\alpha - 4 \dot{\Omega} \Omega^{-1} \tilde{\nabla}_{a}\tilde{\nabla}^{a}\gamma 
\\  \nonumber\\ 
\tilde\nabla^i\Delta_{ij}&=& 2 \dot{\Omega} \Omega^{-1} \tilde{\nabla}_{j}\overset{..}{\gamma} + \Omega^2 \tilde{\nabla}_{j}\delta p^{GI}{} - 2 \dot{\Omega} \Omega^{-1} \tilde{\nabla}_{j}\dot{\alpha} 
\nonumber\\
&&+ (-2 \dot{\Omega}^2 \Omega^{-2} + 4 \overset{..}{\Omega} \Omega^{-1}) \tilde{\nabla}_{j}\dot{\gamma} + (2 k + 2 \dot{\Omega}^2 \Omega^{-2} - 4 \overset{..}{\Omega} \Omega^{-1}) \tilde{\nabla}_{j}\alpha 
\nonumber\\
&&+ 4 \dot{\Omega} k \Omega^{-1} \tilde{\nabla}_{j}\gamma +k \dot{Q}_{j} + 2 \dot{\Omega} k \Omega^{-1} Q_{j} + \tfrac{1}{2} \tilde{\nabla}_{a}\tilde{\nabla}^{a}\dot{Q}_{j} \nonumber \\ 
&& + \dot{\Omega} \Omega^{-1} \tilde{\nabla}_{a}\tilde{\nabla}^{a}Q_{j}
\\  \nonumber\\ 
\tilde\nabla^i\tilde\nabla^j\Delta_{ij}&=& 2 \dot{\Omega} \Omega^{-1} \tilde{\nabla}_{a}\tilde{\nabla}^{a}\overset{..}{\gamma} + \Omega^2 \tilde{\nabla}_{a}\tilde{\nabla}^{a}\delta p^{GI}{} - 2 \dot{\Omega} \Omega^{-1} \tilde{\nabla}_{a}\tilde{\nabla}^{a}\dot{\alpha} 
\nonumber\\
&&+ (-2 \dot{\Omega}^2 \Omega^{-2} + 4 \overset{..}{\Omega} \Omega^{-1}) \tilde{\nabla}_{a}\tilde{\nabla}^{a}\dot{\gamma} \nonumber \\ 
&& + (2 k + 2 \dot{\Omega}^2 \Omega^{-2} - 4 \overset{..}{\Omega} \Omega^{-1}) \tilde{\nabla}_{a}\tilde{\nabla}^{a}\alpha + 4 \dot{\Omega} k \Omega^{-1} \tilde{\nabla}_{a}\tilde{\nabla}^{a}\gamma 
\\  \nonumber\\ 
\tilde\nabla_a\tilde\nabla^a \Delta_{ij}&=& 2 \dot{\Omega} \Omega^{-1} \tilde{g}_{ij} \tilde{\nabla}_{a}\tilde{\nabla}^{a}\overset{..}{\gamma} + \Omega^2 \tilde{g}_{ij} \tilde{\nabla}_{a}\tilde{\nabla}^{a}\delta p^{GI}{} - 2 \dot{\Omega} \Omega^{-1} \tilde{g}_{ij} \tilde{\nabla}_{a}\tilde{\nabla}^{a}\dot{\alpha} \nonumber \\ 
&& + (-2 \dot{\Omega}^2 \Omega^{-2} \tilde{g}_{ij} + 4 \overset{..}{\Omega} \Omega^{-1} \tilde{g}_{ij}) \tilde{\nabla}_{a}\tilde{\nabla}^{a}\dot{\gamma} 
\nonumber\\
&&+ (2 \dot{\Omega}^2 \Omega^{-2} \tilde{g}_{ij} - 4 \overset{..}{\Omega} \Omega^{-1} \tilde{g}_{ij}) \tilde{\nabla}_{a}\tilde{\nabla}^{a}\alpha + \tilde{\nabla}_{a}\tilde{\nabla}^{a}\tilde{\nabla}_{j}\tilde{\nabla}_{i}\alpha \nonumber \\ 
&& + 2 \dot{\Omega} \Omega^{-1} \tilde{\nabla}_{a}\tilde{\nabla}^{a}\tilde{\nabla}_{j}\tilde{\nabla}_{i}\gamma -  \tilde{g}_{ij} \tilde{\nabla}_{b}\tilde{\nabla}^{b}\tilde{\nabla}_{a}\tilde{\nabla}^{a}\alpha 
\nonumber\\
&&- 2 \dot{\Omega} \Omega^{-1} \tilde{g}_{ij} \tilde{\nabla}_{b}\tilde{\nabla}^{b}\tilde{\nabla}_{a}\tilde{\nabla}^{a}\gamma +\tfrac{1}{2} \tilde{\nabla}_{a}\tilde{\nabla}^{a}\tilde{\nabla}_{i}\dot{Q}_{j} \nonumber \\ 
&& + \dot{\Omega} \Omega^{-1} \tilde{\nabla}_{a}\tilde{\nabla}^{a}\tilde{\nabla}_{i}Q_{j} + \tfrac{1}{2} \tilde{\nabla}_{a}\tilde{\nabla}^{a}\tilde{\nabla}_{j}\dot{Q}_{i} + \dot{\Omega} \Omega^{-1} \tilde{\nabla}_{a}\tilde{\nabla}^{a}\tilde{\nabla}_{j}Q_{i}
\nonumber\\
&&- \tilde{\nabla}_{a}\tilde{\nabla}^{a}\overset{..}{E}_{ij} - 2 \dot{\Omega} \Omega^{-1} \tilde{\nabla}_{a}\tilde{\nabla}^{a}\dot{E}_{ij}- 2 k \tilde{\nabla}_{a}\tilde{\nabla}^{a}E_{ij} + \tilde{\nabla}_{b}\tilde{\nabla}^{b}\tilde{\nabla}_{a}\tilde{\nabla}^{a}E_{ij}
\nonumber\\  \\ 
\tilde\nabla_a\tilde\nabla^a \tilde\nabla_b\tilde\nabla^b \Delta_{ij}&=& 2 \dot{\Omega} \Omega^{-1} \tilde{g}_{ij} \tilde{\nabla}_{b}\tilde{\nabla}^{b}\tilde{\nabla}_{a}\tilde{\nabla}^{a}\overset{..}{\gamma} + \Omega^2 \tilde{g}_{ij} \tilde{\nabla}_{b}\tilde{\nabla}^{b}\tilde{\nabla}_{a}\tilde{\nabla}^{a}\delta p^{GI}{} 
\nonumber\\
&&- 2 \dot{\Omega} \Omega^{-1} \tilde{g}_{ij} \tilde{\nabla}_{b}\tilde{\nabla}^{b}\tilde{\nabla}_{a}\tilde{\nabla}^{a}\dot{\alpha}  - 2 \dot{\Omega}^2 \Omega^{-2} \tilde{g}_{ij} \tilde{\nabla}_{b}\tilde{\nabla}^{b}\tilde{\nabla}_{a}\tilde{\nabla}^{a}\dot{\gamma} 
\nonumber\\
&&+ 4 \overset{..}{\Omega} \Omega^{-1} \tilde{g}_{ij} \tilde{\nabla}_{b}\tilde{\nabla}^{b}\tilde{\nabla}_{a}\tilde{\nabla}^{a}\dot{\gamma} + 2 \dot{\Omega}^2 \Omega^{-2} \tilde{g}_{ij} \tilde{\nabla}_{b}\tilde{\nabla}^{b}\tilde{\nabla}_{a}\tilde{\nabla}^{a}\alpha  
\nonumber\\
&&- 4 \overset{..}{\Omega} \Omega^{-1} \tilde{g}_{ij} \tilde{\nabla}_{b}\tilde{\nabla}^{b}\tilde{\nabla}_{a}\tilde{\nabla}^{a}\alpha + \tilde{\nabla}_{b}\tilde{\nabla}^{b}\tilde{\nabla}_{a}\tilde{\nabla}^{a}\tilde{\nabla}_{j}\tilde{\nabla}_{i}\alpha 
\nonumber\\
&&+ 2 \dot{\Omega} \Omega^{-1} \tilde{\nabla}_{b}\tilde{\nabla}^{b}\tilde{\nabla}_{a}\tilde{\nabla}^{a}\tilde{\nabla}_{j}\tilde{\nabla}_{i}\gamma  -  \tilde{g}_{ij} \tilde{\nabla}_{c}\tilde{\nabla}^{c}\tilde{\nabla}_{b}\tilde{\nabla}^{b}\tilde{\nabla}_{a}\tilde{\nabla}^{a}\alpha 
\nonumber\\
&&- 2 \dot{\Omega} \Omega^{-1} \tilde{g}_{ij} \tilde{\nabla}_{c}\tilde{\nabla}^{c}\tilde{\nabla}_{b}\tilde{\nabla}^{b}\tilde{\nabla}_{a}\tilde{\nabla}^{a}\gamma +\tfrac{1}{2} \tilde{\nabla}_{b}\tilde{\nabla}^{b}\tilde{\nabla}_{a}\tilde{\nabla}^{a}\tilde{\nabla}_{i}\dot{Q}_{j} \nonumber \\ 
&& + \dot{\Omega} \Omega^{-1} \tilde{\nabla}_{b}\tilde{\nabla}^{b}\tilde{\nabla}_{a}\tilde{\nabla}^{a}\tilde{\nabla}_{i}Q_{j} + \tfrac{1}{2} \tilde{\nabla}_{b}\tilde{\nabla}^{b}\tilde{\nabla}_{a}\tilde{\nabla}^{a}\tilde{\nabla}_{j}\dot{Q}_{i} 
\nonumber\\
&&+ \dot{\Omega} \Omega^{-1} \tilde{\nabla}_{b}\tilde{\nabla}^{b}\tilde{\nabla}_{a}\tilde{\nabla}^{a}\tilde{\nabla}_{j}Q_{i}- \tilde{\nabla}_{b}\tilde{\nabla}^{b}\tilde{\nabla}_{a}\tilde{\nabla}^{a}\overset{..}{E}_{ij} \nonumber \\ 
&& - 2 \dot{\Omega} \Omega^{-1} \tilde{\nabla}_{b}\tilde{\nabla}^{b}\tilde{\nabla}_{a}\tilde{\nabla}^{a}\dot{E}_{ij} - 2 k \tilde{\nabla}_{b}\tilde{\nabla}^{b}\tilde{\nabla}_{a}\tilde{\nabla}^{a}E_{ij} 
\nonumber\\
&&+ \tilde{\nabla}_{c}\tilde{\nabla}^{c}\tilde{\nabla}_{b}\tilde{\nabla}^{b}\tilde{\nabla}_{a}\tilde{\nabla}^{a}E_{ij}.
\end{eqnarray}
Having obtained the perturbed fluctuation equations expressed entirely in terms of gauge invariants, checking conservation conditions, and generating the higher-derivative equations of motion for testing the decomposition theorem, we conclude our calculation for the standard Einstein fluctuations in the Robertson Walker background geometry. 